Extrinsic Type Inference (DRAFT 2025-06-09)

### 2025-07-10 extrinsic_type_inference_paper/paper.tex
update

\TODO{say what it means simply}
This property is necessary so that our proof typing rules can use positive substitution
as a proxy reasoning under the induction hypothesis.

@@

>>>>

\noindent
The requirement of positive substitution soundness says that
if a variable \ms{\alpha} only occurs in positive positions of a type \ms{\tau},
then the result of the substituting in another type \ms{\tau_r} is weaker than 
any interpretation of the original type \ms{\tau} 
if the replaced variable \ms{\alpha} is interpreted with a type \ms{\tau_l} 
that is weaker than the subbed in type \ms{\tau_r}.
This property is necessary so that our proof typing rules can use positive substitution
as a proxy reasoning under the induction hypothesis without violating soundness.

@@

\TODO{note how substance allows positive packing to place generated constraints into qualified types without violating soundness }
